---
title: "Preliminary NPB Model for Adiposity"
author: "Sheena Martenies"
date: "06/25/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

library(tidyverse)
library(lubridate)
library(haven)
library(readxl)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(family="Calibri",size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
windowsFonts(Calibri=windowsFont("TT Calibri"))
options(scipen = 9999) #avoid scientific notation

geo_data <- "R:/RSTOR-Magzamen/Research/Secondary_Data/ACS_Geodatabases/"
utm_13 <- "+init=epsg:26913"
albers <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
ll_nad83 <- "+proj=longlat +datum=NAD83 +no_defs +ellps=GRS80 +towgs84=0,0,0"
ll_wgs84 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

#' -----------------------------------------------------------------------------
#' Install the new version of the package
#' -----------------------------------------------------------------------------

# library(devtools)
# install_github("lvhoskovec/mmpack", build_vignettes = TRUE, force = TRUE)

library(mmpack)
```

# Exploring the data set

```{r, echo = T, include = F}

#' Read in the clean dataset
hs_data <- read_csv(here::here("Data", "HS_Clean_Data.csv"))
nrow(hs_data)

hs_data2 <- filter(hs_data, include == 1) %>% 
  select(
    #' Exposures
    mean_pm, mean_o3, pct_tree_cover, pct_impervious,
    mean_aadt_intensity, dist_m_tri:dist_m_mine_well, 
    cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
    pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov,
    
    #' Covariates     
    latina_re, black_re, other_re, 
    ed_no_hs, ed_hs, ed_aa, ed_4yr, 
    low_bmi, ovwt_bmi, obese_bmi,
    maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
    male, gest_age_w, days_to_peapod, 
    
    #' Outcomes 
    adiposity) %>% 
  na.omit()
nrow(hs_data2)
```

What percentage of the total HS participants (n = `r nrow(hs_data)`) do we have in this analysis? `r paste0(round((nrow(hs_data2)/ nrow(hs_data)*100),2), "%")`

# Nonparametric Bayesian Shrinkage (NPB): Adiposity

## Exposure data

```{r}
#' Exposure data
X <- select(hs_data2, mean_pm, mean_o3, pct_tree_cover, pct_impervious,
            mean_aadt_intensity, dist_m_tri:dist_m_mine_well,
            cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
            pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov) %>%
  as.matrix()
head(X)
```

Take a look at the covariance in the scaled exposure data

```{r}
var(X)
X.scaled <- apply(X, 2, scale)
var(X.scaled)
```

## Covariate data
References for the indicator variables: white_re, ed_grad, norm_bmi

```{r}
W <- select(hs_data2, latina_re, black_re, other_re,
            ed_no_hs, ed_hs, ed_aa, ed_4yr,
            low_bmi, ovwt_bmi, obese_bmi,
            maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
            male, gest_age_w, days_to_peapod) %>%
  as.matrix()
head(W)
```

Scaled the non-binary (continuous) covariates

```{r}
W.s <- apply(W[,c(11, 14, 15, 17, 18)], 2, scale) #' just the continuous ones

W.scaled <- cbind(W[,1:10], W.s[,1],
                  W[,12:13], W.s[,2:3],
                  W[,16], W.s[,4:5])
colnames(W.scaled)
colnames(W.scaled) <- colnames(W)
head(W.scaled)
summary(W.scaled)

var(W.scaled)
```

## Response data: adiposity

```{r}
Y <- select(hs_data2, adiposity) %>%
  as.matrix()
head(Y)
```

Distribution of adiposity (%fat mass) in our population

```{r}
hist(Y, breaks = 20)
```

## Scatterplots of exposures and outcome (adiposity)

Both adiposity (Y) and the exposures are scaled here

**NOTE**: Don't use these plots as a way to estimate how many predictors might make the cut. This should be done a priori

```{r}
df <- as.data.frame(cbind(scale(Y), X.scaled))
# par(mfrow=c(5,4))
sapply(2:length(df), function(x){
  lm.x <- lm(adiposity ~ df[,x], data = df)
  plot(df[,c(x, 1)],
       xlab = paste0(colnames(df)[x], " beta: ",
                     round(summary(lm.x)$coef[2,1],4)))
  abline(lm.x)
})
```

# Finding the NPB priors

Start with Lauren's from the example in the vignette

In an email from April 29, Lauren provided me with some additional guidance
on finding the NPB priors:

- Keep alpha.pi and beta.pi set to 1, and then let a.phi1 take values 1, 10, and 100 and see how the results change.
- Keep a.phi1 set to 1 (or 10 or 100), and mess with alpha.pi and beta.pi.
    - Run the following code:
       alpha.pi=1
       beta.pi=1
       plot(density(rbeta(10000, alpha.pi, beta.pi)))
       and then change alpha.pi and beta.pi and see how it changes the prior distribution.
    - This is the distribution of the probability of a main effect regression coefficient being 0 (aka exclusion probability). We don't want this to be too informative (you don't want high mass around just a few values). Also alpha.pi and beta.pi don't have to be the same value. You might try alpha.pi = 1 and beta.pi = 2 to get a slightly lower prior probability of exclusion. Try not to change all three (alpha.pi, beta.pi, and a.phi1) at once.
- When playing with the priors, set "interact=FALSE" and just fit the modelwith the main effects. Most of the interactions were null anyway so it shouldn't change the results too much and it will make the code run a lot faster. Then when you find a set of priors you like, you can add in "interact=TRUE" and "XWinteract=TRUE."

Some additional feedback from Lauren during our 6/10 meeting:

- The confidence intervals were really wide and heavily skewed. I'm going to try adjusting the sig2inv.mu1 parameter after the a.phi1 parameter to see if this helps
- the rbeta distributions is interpreted as the exclusion probability, so I should try to aim to have most of the mass of that distribution in the middle, since we hypothesize that maybe 40-60% of the predictors will be important. The way to do this is to set alpha.pi and beta.pi to the same value
- I should set the burn in number to be about half the iterations

## Vignette Priors

```{r}
set.seed(123)

priors.npb.1 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1)

fit.npb.1 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.1, interact = F)
npb.sum.1 <- summary(fit.npb.1)
npb.sum.1$main.effects
plot(fit.npb.1$beta[,1], type = "l")
plot(fit.npb.1$beta[,2], type = "l")
plot(fit.npb.1$beta[,13], type = "l")
```

## Adjust sig2inv.mu1

The default value for this parameter is 1.
Adjusting this parameter may help narrow these confidence intervals a bit

### Try sig2inv.mu1 = 10

That seemed to make the confidence intervals wider

```{r}
priors.npb.2 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     sig2inv.mu1 = 10)

fit.npb.2 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.2, interact = F)
npb.sum.2 <- summary(fit.npb.2)
npb.sum.2$main.effects
plot(fit.npb.2$beta[,1], type = "l")
plot(fit.npb.2$beta[,2], type = "l")
plot(fit.npb.2$beta[,13], type = "l")
```

### Try sig2inv.mu1 = 100

That also seemed to make the confidence intervals wider

```{r}
priors.npb.3 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     sig2inv.mu1 = 100)

fit.npb.3 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.3, interact = F)
npb.sum.3 <- summary(fit.npb.3)
npb.sum.3$main.effects
plot(fit.npb.3$beta[,1], type = "l")
plot(fit.npb.3$beta[,2], type = "l")
plot(fit.npb.3$beta[,13], type = "l")
```

### Try sig2inv.mu1 = 0.1?

This might be too narrow?

```{r}
priors.npb.4 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     sig2inv.mu1 = 0.1)

fit.npb.4 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.4, interact = F)
npb.sum.4 <- summary(fit.npb.4)
npb.sum.4$main.effects
plot(fit.npb.4$beta[,1], type = "l")
plot(fit.npb.4$beta[,2], type = "l")
plot(fit.npb.4$beta[,13], type = "l")
```

### Try sig2inv.mu1 = 0.5?

Also too narrow-- going back to 1

```{r}
priors.npb.4 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     sig2inv.mu1 = 0.1)

fit.npb.4 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.4, interact = F)
npb.sum.4 <- summary(fit.npb.4)
npb.sum.4$main.effects
plot(fit.npb.4$beta[,1], type = "l")
plot(fit.npb.4$beta[,2], type = "l")
plot(fit.npb.4$beta[,13], type = "l")
```

## Next, try adjusting a.phi1

This parameter is the shape parameter for gamma prior on phi sub1 inv2.
It's default value is 1

### Try making a.phi1 = 10
PIPs again increase slightly

```{r}
priors.npb.5 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10)

fit.npb.5 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.5, interact = F)
npb.sum.5 <- summary(fit.npb.5)
npb.sum.5$main.effects
plot(fit.npb.5$beta[,1], type = "l")
plot(fit.npb.5$beta[,2], type = "l")
plot(fit.npb.5$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 10

Definitely worse in terms of the confidence intervals

```{r}
priors.npb.6 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 10)

fit.npb.6 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.6, interact = F)
npb.sum.6 <- summary(fit.npb.6)
npb.sum.6$main.effects
plot(fit.npb.6$beta[,1], type = "l")
plot(fit.npb.6$beta[,2], type = "l")
plot(fit.npb.6$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 100

Not an improvement

```{r}
priors.npb.7 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 100)

fit.npb.7 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.7, interact = F)
npb.sum.7 <- summary(fit.npb.7)
npb.sum.7$main.effects
plot(fit.npb.7$beta[,1], type = "l")
plot(fit.npb.7$beta[,2], type = "l")
plot(fit.npb.7$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 0.1

Nope

```{r}
priors.npb.8 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 0.1)

fit.npb.8 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.8, interact = F)
npb.sum.8 <- summary(fit.npb.8)
npb.sum.8$main.effects
plot(fit.npb.8$beta[,1], type = "l")
plot(fit.npb.8$beta[,2], type = "l")
plot(fit.npb.8$beta[,13], type = "l")
```

### Try making a.phi1 = 100

```{r}
priors.npb.9 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 1)

fit.npb.9 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.9, interact = F)
npb.sum.9 <- summary(fit.npb.9)
npb.sum.9$main.effects
plot(fit.npb.9$beta[,1], type = "l")
plot(fit.npb.9$beta[,2], type = "l")
plot(fit.npb.9$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 10

```{r}
priors.npb.10 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 10)

fit.npb.10 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.10, interact = F)
npb.sum.10 <- summary(fit.npb.10)
npb.sum.10$main.effects
plot(fit.npb.10$beta[,1], type = "l")
plot(fit.npb.10$beta[,2], type = "l")
plot(fit.npb.10$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 100

Still not great.

```{r}
priors.npb.11 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 100)

fit.npb.11 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.11, interact = F)
npb.sum.11 <- summary(fit.npb.11)
npb.sum.11$main.effects
plot(fit.npb.11$beta[,1], type = "l")
plot(fit.npb.11$beta[,2], type = "l")
plot(fit.npb.11$beta[,13], type = "l")
```

## Adjust alpha.pi and beta.pi

For now, leave a.phi1 and sig2inv.mu1 alone for now.

alpha.pi and beta.pi are responisble for the exclusion probability distribution.
If we thing we want ~50% of our covariates, we need the mass of this distribution to be somewhere between 0.4 and 0.6. To do this, we set alpha.pi and beta.pi to the same value

### Try making alpha.pi and beta.pi 2

```{r}
plot(density(rbeta(10000, 2, 2)))

priors.npb.12 <- list(alpha.pi = 2, beta.pi = 2, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.12 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.12, interact = F)
npb.sum.12 <- summary(fit.npb.12)
npb.sum.12$main.effects
plot(fit.npb.12$beta[,1], type = "l")
plot(fit.npb.12$beta[,2], type = "l")
plot(fit.npb.12$beta[,13], type = "l")
```

### Try making alpha.pi and beta.pi 5

```{r}
plot(density(rbeta(10000, 5, 5)))

priors.npb.13 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.13 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.13, interact = F)
npb.sum.13 <- summary(fit.npb.13)
npb.sum.13$main.effects
plot(fit.npb.13$beta[,1], type = "l")
plot(fit.npb.13$beta[,2], type = "l")
plot(fit.npb.13$beta[,13], type = "l")
```

### Try making alpha.pi and beta.pi 8

```{r}
plot(density(rbeta(10000, 8, 8)))

priors.npb.14 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.14 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.14, interact = F)
npb.sum.14 <- summary(fit.npb.14)
npb.sum.14$main.effects
plot(fit.npb.14$beta[,1], type = "l")
plot(fit.npb.14$beta[,2], type = "l")
plot(fit.npb.14$beta[,13], type = "l")
```

### Try making alpha.pi and beta.pi 10

This might be getting too big... Is there enough space in the tails?

```{r}
plot(density(rbeta(10000, 10, 10)))

priors.npb.15 <- list(alpha.pi = 10, beta.pi = 10, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.15 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.15, interact = F)
npb.sum.15 <- summary(fit.npb.15)
npb.sum.15$main.effects
plot(fit.npb.15$beta[,1], type = "l")
plot(fit.npb.15$beta[,2], type = "l")
plot(fit.npb.15$beta[,13], type = "l")
```

## Set alpha.pi and beta.pi to 8, readjust a.phi1 and sig2inv.mu1

Set  alpha.pi and beta.pi to 8, try adjusting a.phi1 and sig2inv.mu1

### Try making a.phi1 = 10 and sig2inv.mu1 = 1

```{r}
priors.npb.16 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.16 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.16, interact = F)
npb.sum.16 <- summary(fit.npb.16)
npb.sum.16$main.effects
plot(fit.npb.16$beta[,1], type = "l")
plot(fit.npb.16$beta[,2], type = "l")
plot(fit.npb.16$beta[,13], type = "l")
```

Same priors, but now with ```scaleY = F```

```{r}
priors.npb.16a <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.16a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.16a, interact = F)
npb.sum.16a <- summary(fit.npb.16a)
npb.sum.16a$main.effects
plot(fit.npb.16a$beta[,1], type = "l")
plot(fit.npb.16a$beta[,2], type = "l")
plot(fit.npb.16a$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 10

```{r}
priors.npb.17 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 10)

fit.npb.17 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.17, interact = F)
npb.sum.17 <- summary(fit.npb.17)
npb.sum.17$main.effects
plot(fit.npb.17$beta[,1], type = "l")
plot(fit.npb.17$beta[,2], type = "l")
plot(fit.npb.17$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 100

```{r}
priors.npb.18 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 100)

fit.npb.18 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.18, interact = F)
npb.sum.18 <- summary(fit.npb.18)
npb.sum.18$main.effects
plot(fit.npb.18$beta[,1], type = "l")
plot(fit.npb.18$beta[,2], type = "l")
plot(fit.npb.18$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 1

```{r}
priors.npb.19 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 1)

fit.npb.19 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.19, interact = F)
npb.sum.19 <- summary(fit.npb.19)
npb.sum.19$main.effects
plot(fit.npb.19$beta[,1], type = "l")
plot(fit.npb.19$beta[,2], type = "l")
plot(fit.npb.19$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 10

```{r}
priors.npb.20 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 10)

fit.npb.20 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.20, interact = F)
npb.sum.20 <- summary(fit.npb.20)
npb.sum.20$main.effects
plot(fit.npb.20$beta[,1], type = "l")
plot(fit.npb.20$beta[,2], type = "l")
plot(fit.npb.20$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 100

```{r}
priors.npb.21 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 100)

fit.npb.21 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.21, interact = F)
npb.sum.21 <- summary(fit.npb.21)
npb.sum.21$main.effects
plot(fit.npb.21$beta[,1], type = "l")
plot(fit.npb.21$beta[,2], type = "l")
plot(fit.npb.21$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.21a <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 100)

fit.npb.21a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = F,
                 priors = priors.npb.21a, interact = F)
npb.sum.21a <- summary(fit.npb.21a)
npb.sum.21a$main.effects
plot(fit.npb.21a$beta[,1], type = "l")
plot(fit.npb.21a$beta[,2], type = "l")
plot(fit.npb.21a$beta[,13], type = "l")
```

### Try making a.phi1 = 10e5 and sig2inv.mu1 = 10e5

```{r}
priors.npb.22 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10e5, sig2inv.mu1 = 10e5)

fit.npb.22 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.22, interact = F)
npb.sum.22 <- summary(fit.npb.22)
npb.sum.22$main.effects
plot(fit.npb.22$beta[,1], type = "l")
plot(fit.npb.22$beta[,2], type = "l")
plot(fit.npb.22$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.22a <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10e5, sig2inv.mu1 = 10e5)

fit.npb.22a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.22a, interact = F)
npb.sum.22a <- summary(fit.npb.22a)
npb.sum.22a$main.effects
plot(fit.npb.22a$beta[,1], type = "l")
plot(fit.npb.22a$beta[,2], type = "l")
plot(fit.npb.22a$beta[,13], type = "l")
```

## Set alpha.pi and beta.pi to 5, readjust a.phi1 and sig2inv.mu1

Set alpha.pi and beta.pi to 5, rather than 8, and try adjusting a.phi1 and sig2inv.mu1

### Try making a.phi1 = 10 and sig2inv.mu1 = 1

```{r}
priors.npb.23 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.23 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.23, interact = F)
npb.sum.23 <- summary(fit.npb.23)
npb.sum.23$main.effects
plot(fit.npb.23$beta[,1], type = "l")
plot(fit.npb.23$beta[,2], type = "l")
plot(fit.npb.23$beta[,13], type = "l")
```

Same priors, but now with ```scaleY = F```

```{r}
priors.npb.23a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.23a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.23a, interact = F)
npb.sum.23a <- summary(fit.npb.23a)
npb.sum.23a$main.effects
plot(fit.npb.23a$beta[,1], type = "l")
plot(fit.npb.23a$beta[,2], type = "l")
plot(fit.npb.23a$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 10

```{r}
priors.npb.24 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 10)

fit.npb.24 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.24, interact = F)
npb.sum.24 <- summary(fit.npb.24)
npb.sum.24$main.effects
plot(fit.npb.24$beta[,1], type = "l")
plot(fit.npb.24$beta[,2], type = "l")
plot(fit.npb.24$beta[,13], type = "l")
```

### Try making a.phi1 = 10 and sig2inv.mu1 = 100

```{r}
priors.npb.25 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 100)

fit.npb.25 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.25, interact = F)
npb.sum.25 <- summary(fit.npb.25)
npb.sum.25$main.effects
plot(fit.npb.25$beta[,1], type = "l")
plot(fit.npb.25$beta[,2], type = "l")
plot(fit.npb.25$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 1

```{r}
priors.npb.26 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 1)

fit.npb.26 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.26, interact = F)
npb.sum.26 <- summary(fit.npb.26)
npb.sum.26$main.effects
plot(fit.npb.26$beta[,1], type = "l")
plot(fit.npb.26$beta[,2], type = "l")
plot(fit.npb.26$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 10

```{r}
priors.npb.27 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 10)

fit.npb.27 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.27, interact = F)
npb.sum.27 <- summary(fit.npb.27)
npb.sum.27$main.effects
plot(fit.npb.27$beta[,1], type = "l")
plot(fit.npb.27$beta[,2], type = "l")
plot(fit.npb.27$beta[,13], type = "l")
```

### Try making a.phi1 = 100 and sig2inv.mu1 = 100

```{r}
priors.npb.28 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 100)

fit.npb.28 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.28, interact = F)
npb.sum.28 <- summary(fit.npb.28)
npb.sum.28$main.effects
plot(fit.npb.28$beta[,1], type = "l")
plot(fit.npb.28$beta[,2], type = "l")
plot(fit.npb.28$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.28a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 100, sig2inv.mu1 = 100)

fit.npb.28a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = F,
                 priors = priors.npb.28a, interact = F)
npb.sum.28a <- summary(fit.npb.28a)
npb.sum.28a$main.effects
plot(fit.npb.28a$beta[,1], type = "l")
plot(fit.npb.28a$beta[,2], type = "l")
plot(fit.npb.28a$beta[,13], type = "l")
```

### Try making a.phi1 = 10e5 and sig2inv.mu1 = 10e5

```{r}
priors.npb.29 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10e5, sig2inv.mu1 = 10e5)

fit.npb.29 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.29, interact = F)
npb.sum.29 <- summary(fit.npb.29)
npb.sum.29$main.effects
plot(fit.npb.29$beta[,1], type = "l")
plot(fit.npb.29$beta[,2], type = "l")
plot(fit.npb.29$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.29a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10e5, sig2inv.mu1 = 10e5)

fit.npb.29a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.29a, interact = F)
npb.sum.29a <- summary(fit.npb.29a)
npb.sum.29a$main.effects
plot(fit.npb.29a$beta[,1], type = "l")
plot(fit.npb.29a$beta[,2], type = "l")
plot(fit.npb.29a$beta[,13], type = "l")
```

## Set alpha.pi and beta.pi to 5, set a.phi1 = 1, and adjust sig2inv.mu1

### Try making a.phi1 = 1 and sig2inv.mu1 = 10

```{r}
priors.npb.30 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 10)

fit.npb.30 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.30, interact = F)
npb.sum.30 <- summary(fit.npb.30)
npb.sum.30$main.effects
plot(fit.npb.30$beta[,1], type = "l")
plot(fit.npb.30$beta[,2], type = "l")
plot(fit.npb.30$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.30a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 10)

fit.npb.30a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.30a, interact = F)
npb.sum.30a <- summary(fit.npb.30a)
npb.sum.30a$main.effects
plot(fit.npb.30a$beta[,1], type = "l")
plot(fit.npb.30a$beta[,2], type = "l")
plot(fit.npb.30a$beta[,13], type = "l")
```

### Try making a.phi1 = 1 and sig2inv.mu1 = 100

```{r}
priors.npb.31 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 100)

fit.npb.31 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.31, interact = F)
npb.sum.31 <- summary(fit.npb.31)
npb.sum.31$main.effects
plot(fit.npb.31$beta[,1], type = "l")
plot(fit.npb.31$beta[,2], type = "l")
plot(fit.npb.31$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.31a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 100)

fit.npb.31a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.31a, interact = F)
npb.sum.31a <- summary(fit.npb.31a)
npb.sum.31a$main.effects
plot(fit.npb.31a$beta[,1], type = "l")
plot(fit.npb.31a$beta[,2], type = "l")
plot(fit.npb.31a$beta[,13], type = "l")
```

### Try making a.phi1 = 1 and sig2inv.mu1 = 10e5

```{r}
priors.npb.32 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 10e5)

fit.npb.32 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = TRUE,
                 priors = priors.npb.32, interact = F)
npb.sum.32 <- summary(fit.npb.32)
npb.sum.32$main.effects
plot(fit.npb.32$beta[,1], type = "l")
plot(fit.npb.32$beta[,2], type = "l")
plot(fit.npb.32$beta[,13], type = "l")
```

Same priors, but with scaleY = F

```{r}
priors.npb.32a <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 10e5)

fit.npb.32a <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled,
                 scaleY = FALSE,
                 priors = priors.npb.32a, interact = F)
npb.sum.32a <- summary(fit.npb.32a)
npb.sum.32a$main.effects
plot(fit.npb.32a$beta[,1], type = "l")
plot(fit.npb.32a$beta[,2], type = "l")
plot(fit.npb.32a$beta[,13], type = "l")
```

# Select a set of priors and fit the NPB model
Below I've used the 21st set of priors and set ```scaleY = T```

```{r}
priors.npb <- priors.npb.21

fit.npb <- npb(niter = 10000, nburn = 1000, X = X.scaled, Y = Y, W = W.scaled,
               scaleY = TRUE,
               priors = priors.npb, interact = TRUE, XWinteract = TRUE)
save(fit.npb, file = here::here("Results", "NPB_Adiposity.rdata"))

# load(here::here("Results", "NPB_Adiposity.rdata"))
npb.sum <- summary(fit.npb)
```

## First, main effect regression coefficients with PIPs

```{r}
npb.sum$main.effects
selected_exp <- which(npb.sum$main.effects[,5] >= 0.5)
selected_exp

#' Which variables are these?
exp_names <- colnames(X)[selected_exp]
exp_names
```

## Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum$interactions
```

## Predict fitted values for each individual

```{r}
pred.npb <- predict(fit.npb)
fittedvals <- pred.npb$fitted.vals
```

## Plot predicted outcomes against "measured" outcomes

```{r}
plot(fittedvals, Y)
abline(a = 0, b = 1, col = "red")
```
