---
title: "NPB Model for Birth Weight"
author: "Sheena Martenies"
date: "02/10/2021"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r}
#' -----------------------------------------------------------------------------
#' Install the new version of the package
#' -----------------------------------------------------------------------------

#library(devtools)
#install_github("lvhoskovec/mmpack", build_vignettes = TRUE, force = TRUE)

library(tidyverse)
library(lubridate)
library(haven)
library(readxl)
library(mmpack)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(family="Calibri",size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
# windowsFonts(Calibri=windowsFont("TT Calibri"))
options(scipen = 9999) #avoid scientific notation

set.seed(123)

```

<!-- In this version of the analysis, we wanted to try a few things to refine our model and check some things out. After meeting with Ander, Lauren, and Sheryl, here's what we've come up with: -->

<!-- - The effect of ozone seen in the previous version of the model might actually be a seasonal signal. I'm going to add indicator variables for season of conception -->
<!-- - Residual spatial confounding is also an issue given the spatial patterns in both the environmental (esp. ozone) and social exposures. We're addressing this in two ways: -->
<!--     - First, we're adding lon, lat, and lon*lat to the covariates matrix -->
<!--     - Second, we're adding census tract percent POC (Total Pop - NHW / Total Pop * 100) to the exposures -->
<!-- - In order to better compare the RIDGE and NPB models, I'm generating rescaled estimates and 95% CIs for the RIDGE coefficients -->

<!-- We also wanted to try rerunning the BKMR model with exposures selected by the NPB model. If we have 3 predictors with a PIP > 0.5 (or close to it), we can include them in a BKMR. Alternatively, for 1-2 exposures, we can just look at a GAM -->

<!-- Lauren is going to add a frame to the summary() function that will give us posterior means and CIs for the covariates (but they won't have PIPs) -->

# Exploring the data set

The HS data set was previously used in the CEI paper (Martenies et al., 2019). In the original analysis, we used an exposure index based on the CalEnvironScreen tool. We observed lower birth weights and lower adiposity associated with higher index scores, driven largely by exposures to social indicators of health at the neighborhood level. Now, we are aiming to use methods for mixtures to try to identify which exposures are driving these association.

```{r, echo = T, include = F}

#' Read in the clean dataset
hs_data <- read_csv(here::here("Data", "HS_Clean_Data.csv")) %>% 
  filter(!is.na(conception_date))
nrow(hs_data)

#' Add some additional variables
hs_data$lat_lon_int <- hs_data$lat * hs_data$lon
hs_data$concep_year <- year(hs_data$conception_date)
hs_data$dob <- hs_data$mrdata17

unique(hs_data$concep_year)

hs_data$concep_2009 <- ifelse(hs_data$concep_year == "2009", 1, 0)
hs_data$concep_2010 <- ifelse(hs_data$concep_year == "2010", 1, 0)
hs_data$concep_2011 <- ifelse(hs_data$concep_year == "2011", 1, 0)
hs_data$concep_2012 <- ifelse(hs_data$concep_year == "2012", 1, 0)
hs_data$concep_2013 <- ifelse(hs_data$concep_year == "2013", 1, 0)

hs_data1 <- filter(hs_data, include == 1)

hs_data2 <- filter(hs_data, include == 1) %>% 
  select(
    #' Exposures
    mean_pm, mean_o3, mean_temp, pct_tree_cover, pct_impervious,
    mean_aadt_intensity, dist_m_tri:dist_m_mine_well, 
    cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
    pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov, pct_poc,
    
    #' Covariates     
    lon, lat, lat_lon_int, 
    latina_re, black_re, other_re, #' ref is white_re
    ed_no_hs, ed_hs, ed_aa, ed_4yr, #' ref is ed_grad
    low_bmi, ovwt_bmi, obese_bmi, #' ref is norm_bmi
    concep_spring, concep_summer, concep_fall, #' ref is concep_winter
    concep_2010, concep_2011, concep_2012, concep_2013, #ref is concep_2009
    maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
    male, gest_age_w, 
    
    #' Outcomes 
    birth_weight) %>% 
  na.omit()
```

The complete data set for the birth weight outcome consists of n =  `r nrow(hs_data2)` participants. This represents `r paste0(round((nrow(hs_data2)/ nrow(hs_data)*100),2), "%")` of the original Healthy Start 1 cohort.

Of the `r nrow(hs_data2)` participants, `r round(sum(hs_data2$latina_re)/nrow(hs_data2),2)*100`% identify as Latina, `r round(sum(hs_data2$black_re)/nrow(hs_data2),2)*100`% identify as Black, and `r round(sum(hs_data2$latina_re)/nrow(hs_data2),2)*100`% identify as another non-NHW race or ethnicity. The median age of mothers in this dataset is `r round(median(hs_data2$maternal_age),2)` years.  `r round(sum(hs_data2$male)/nrow(hs_data2),2)*100`% of babies born were male.  

## Effect of year on birth weight

The following examines whether there are trends in birth weight by year of birth.

```{r}
plot(hs_data1$dob, hs_data1$birth_weight)
abline(lm(birth_weight ~ dob, data = hs_data1), col = "red")
```

Grouping birth weights by conception year doesn't show much of a trend:

```{r}
bw_trends_by_concept <- ggplot(data = hs_data1) +
  geom_boxplot(aes(x = concep_year, group = concep_year, y = birth_weight))
bw_trends_by_concept
```

## Exposure data

We have included `r ncol(select(hs_data2, mean_pm:pct_hh_pov))` exposures in our analysis. 

These exposures are based on the census tract where each mother lived at the time of enrollment into Healthy Start. With the exception of air pollution (mean_pm and mean_o3) and temperature, these are based on long-term averages at for each census tract. For the air pollutants and temerature variables, we used the average pollution levels across each pregnancy (est. conception date to delivery date) estimated using ordinary kriging and monitoring data.

```{r}
#' Exposure data
X <- select(hs_data2, mean_pm, mean_o3, mean_temp, pct_tree_cover, pct_impervious,
            mean_aadt_intensity, dist_m_tri:dist_m_mine_well,
            cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
            pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov, pct_poc) %>%
  as.matrix()
head(X)
```

Variance and histograms of the exposure variables (in their original units):

```{r}
var(X)
ggplot(pivot_longer(as.data.frame(X), mean_pm:pct_poc, names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

Scaling the exposure variables

```{r}
X.scaled <- apply(X, 2, scale)
head(X.scaled)
```

Variance and histograms of the exposure variables (scaled):

```{r}
var(X.scaled)
ggplot(pivot_longer(as.data.frame(X.scaled), mean_pm:pct_poc, 
                    names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

## Covariate data

Covariates were assessed at the individual level. These were selected based on previous HS studies and others in the literature and informed by a DAG.

```{r}
W <- select(hs_data2, 
            lat, lon, lat_lon_int,
            latina_re, black_re, other_re,
            ed_no_hs, ed_hs, ed_aa, ed_4yr,
            low_bmi, ovwt_bmi, obese_bmi,
            concep_spring, concep_summer, concep_fall,
            concep_2010, concep_2011, concep_2012, concep_2013,
            maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
            male, gest_age_w) %>%
  as.matrix()
head(W)
```

Scaled the non-binary (continuous) covariates

```{r}
colnames(W)
W.s <- apply(W[,c(1, 2, 3, 21, 24, 25, 27)], 2, scale) #' just the continuous ones

W.scaled <- cbind(W.s[,1:3],
                  W[,4:20], W.s[,4],
                  W[,22:23], W.s[,5:6],
                  W[,26], W.s[,7])
colnames(W.scaled)
colnames(W.scaled) <- colnames(W)
head(W.scaled)
summary(W.scaled)
```

Variance and histograms for the scaled covariates

```{r}
var(W.scaled)

ggplot(pivot_longer(as.data.frame(W.scaled), lat:gest_age_w, 
                    names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

## Response data: birth weight (in grams)

```{r}
Y <- select(hs_data2, birth_weight) %>%
  as.matrix()
head(Y)
```

Distribution of birth weight and scaled birth weight

```{r}
hist(Y, breaks = 20)
hist(scale(Y), breaks = 20)
```

## Scatterplots of exposures and outcome (birth weight)

Both birth weight (Y) and the exposures are scaled here

**NOTE**: Don't use these plots as a way to estimate how many predictors might make the cut. This should be done a priori

```{r}
df <- as.data.frame(cbind(scale(Y), X.scaled))
# par(mfrow=c(5,4))
sapply(2:length(df), function(x){
  lm.x <- lm(birth_weight ~ df[,x], data = df)
  plot(df[,c(x, 1)],
       xlab = paste0(colnames(df)[x], " beta: ",
                     round(summary(lm.x)$coef[2,1],4),
                     "; p = ",
                     round(summary(lm.x)$coef[2,4],4)))
  abline(lm.x)
})
```

# Is gestational age a potenital mediator?

I.e., is there a relationship between our exposures and gestational age?

The DAG might look something like this:

exposures ---> gestational age ---> birth weight
     \ _________________________________^

## Scatter plots for exposures and gestational age

Both gestational age and the exposures are scaled here.
Gestational age measured in weeks from estimated date of conception to delivery

Since there were some (small) relationships between exposures and gestational age (based on simple linear regression models-- namely the ozone and SES indicators), I'm going to omit this covariate for now. 

```{r}
df2 <- as.data.frame(cbind(W.scaled[,"gest_age_w"], X.scaled))
colnames(df2)[1] <- "gest_age_w"
# par(mfrow=c(5,4))
sapply(2:length(df2), function(x){
  lm.x <- lm(gest_age_w ~ df2[,x], data = df2)
  plot(df2[,c(x, 1)],
       xlab = paste0(colnames(df2)[x], " beta: ",
                     round(summary(lm.x)$coef[2,1],4),
                     "; p = ",
                     round(summary(lm.x)$coef[2,4],4)))
  abline(lm.x)
})
```

Dropping gest_age_w from the covariates

```{r}
colnames(W.scaled)
W.scaled2 <- W.scaled[,-c(ncol(W.scaled))]
colnames(W.scaled2)
```

# RIDGE regression

To see if there might be something going on, Lauren suggested a ridge regression with a small penalty.

```{r}
set.seed(123)

library(glmnet)

lambda_seq <- 10^seq(4, -4, by = -.05)

#' Best lambda from CV
ridge_cv <- cv.glmnet(X, Y, alpha = 0, lambda = lambda_seq,
                      standardize = T, standardize.response = T)
plot(ridge_cv)
best_lambda <- ridge_cv$lambda.min
best_lambda

#' Fit the model using the best_lambda
bw_ridge <- glmnet(X, Y, alpha = 0, lambda = best_lambda,
                   standardize = T, standardize.response = T)
summary(bw_ridge)
```

Ridge regression coefficients

```{r}
coef(bw_ridge)
```

Ridge regression predictions

```{r}
ridge_pred <- predict(bw_ridge, newx = X)
plot(Y, ridge_pred)

actual <- Y
preds <- ridge_pred
rsq <- 1 - (sum((preds - actual) ^ 2))/(sum((actual - mean(actual)) ^ 2))
```

The R2 value for this model is `r round(rsq, 2)`. Based on these results, it doesn't look like there's much here.

# Nonparametric Bayesian Shrinkage (NPB): Birth weight

Still, we wanted to try to fit the NPB model with these data.

## Finding the NPB priors

Start with Lauren's from the example in the vignette

In an email from April 29, Lauren provided me with some additional guidance
on finding the NPB priors:

- Keep alpha.pi and beta.pi set to 1, and then let a.phi1 take values 1, 10, and 100 and see how the results change.
- Keep a.phi1 set to 1 (or 10 or 100), and mess with alpha.pi and beta.pi.
    - Run the following code:
       alpha.pi=1
       beta.pi=1
       plot(density(rbeta(10000, alpha.pi, beta.pi)))
       and then change alpha.pi and beta.pi and see how it changes the prior distribution.
    - This is the distribution of the probability of a main effect regression coefficient being 0 (aka exclusion probability). We don't want this to be too informative (you don't want high mass around just a few values). Also alpha.pi and beta.pi don't have to be the same value. You might try alpha.pi = 1 and beta.pi = 2 to get a slightly lower prior probability of exclusion. Try not to change all three (alpha.pi, beta.pi, and a.phi1) at once.
- When playing with the priors, set "interact=FALSE" and just fit the modelwith the main effects. Most of the interactions were null anyway so it shouldn't change the results too much and it will make the code run a lot faster. Then when you find a set of priors you like, you can add in "interact=TRUE" and "XWinteract=TRUE."

Some additional feedback from Lauren during our 6/10 meeting:

- The confidence intervals were really wide and heavily skewed. I'm going to try adjusting the sig2inv.mu1 parameter after the a.phi1 parameter to see if this helps
- the rbeta distributions is interpreted as the exclusion probability, so I should try to aim to have most of the mass of that distribution in the middle, since we hypothesize that maybe 40-60% of the predictors will be important. The way to do this is to set alpha.pi and beta.pi to the same value
- I should set the burn in number to be about half the iterations

**Note**: I'm including far fewer iterations of the priors than in the previous version of the document.

### Vignette Priors

```{r}
set.seed(123)

priors.npb.1 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1)

fit.npb.1 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.1, interact = F)
npb.sum.1 <- summary(fit.npb.1)
npb.sum.1$main.effects
plot(fit.npb.1$beta[,1], type = "l")
plot(fit.npb.1$beta[,2], type = "l")
plot(fit.npb.1$beta[,13], type = "l")
```

### Adjust alpha.pi and beta.pi

For now, leave a.phi1 and sig2inv.mu1 alone for now.

alpha.pi and beta.pi are responsible for the exclusion probability distribution.
If we think we want ~50% of our covariates, we need the mass of this distribution to be somewhere between 0.4 and 0.6. To do this, we set alpha.pi and beta.pi to the same value

#### Try making alpha.pi and beta.pi 2

```{r}
plot(density(rbeta(10000, 2, 2)))

priors.npb.12 <- list(alpha.pi = 2, beta.pi = 2, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.12 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.12, interact = F)
npb.sum.12 <- summary(fit.npb.12)
npb.sum.12$main.effects
plot(fit.npb.12$beta[,1], type = "l")
plot(fit.npb.12$beta[,2], type = "l")
plot(fit.npb.12$beta[,13], type = "l")
```

#### Try making alpha.pi and beta.pi 5

```{r}
plot(density(rbeta(10000, 5, 5)))

priors.npb.13 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.13 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.13, interact = F)
npb.sum.13 <- summary(fit.npb.13)
npb.sum.13$main.effects
plot(fit.npb.13$beta[,1], type = "l")
plot(fit.npb.13$beta[,2], type = "l")
plot(fit.npb.13$beta[,13], type = "l")
```

#### Try making alpha.pi and beta.pi 8

```{r}
plot(density(rbeta(10000, 8, 8)))

priors.npb.14 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.14 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.14, interact = F)
npb.sum.14 <- summary(fit.npb.14)
npb.sum.14$main.effects
plot(fit.npb.14$beta[,1], type = "l")
plot(fit.npb.14$beta[,2], type = "l")
plot(fit.npb.14$beta[,13], type = "l")
```

### Set alpha.pi and beta.pi to 5, readjust a.phi1 and sig2inv.mu1

Set alpha.pi and beta.pi to 5, rather than 8, and try adjusting a.phi1 and sig2inv.mu1

#### Try making a.phi1 = 10 and sig2inv.mu1 = 1

```{r}
priors.npb.23 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.23 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.23, interact = F)
npb.sum.23 <- summary(fit.npb.23)
npb.sum.23$main.effects
plot(fit.npb.23$beta[,1], type = "l")
plot(fit.npb.23$beta[,2], type = "l")
plot(fit.npb.23$beta[,13], type = "l")
```

#### Try making a.phi1 = 10 and sig2inv.mu1 = 10

```{r}
priors.npb.24 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 10)

fit.npb.24 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.24, interact = F)
npb.sum.24 <- summary(fit.npb.24)
npb.sum.24$main.effects
plot(fit.npb.24$beta[,1], type = "l")
plot(fit.npb.24$beta[,2], type = "l")
plot(fit.npb.24$beta[,13], type = "l")
```

## Fit the NPB model without temperature

Below I've used the set of priors labeled "24" and set ```scaleY = T```

The priors are as follows:
```r priors.npb.24```

Note that this version of the model **does not** include gest_age_w. It does include an indicator variable for season of conception (ref = winter) and the lon/lat as covariates and the percentage of the census tract population that is not NHW as an exposure.

```{r}
priors.npb <- priors.npb.24

#' Exposures (minus temperature)
colnames(X.scaled)

#' Covariates
colnames(W.scaled2)

# fit.npb <- npb(niter = 5000, nburn = 2500, X = X.scaled[,-c(3)], Y = Y, W = W.scaled2,
#                scaleY = TRUE,
#                priors = priors.npb, interact = TRUE, XWinteract = TRUE)
# save(fit.npb, file = here::here("Results", "NPB_Birth_Weight_v4.1.rdata"))

load(here::here("Results", "NPB_Birth_Weight_v4.1.rdata"))
npb.sum <- summary(fit.npb)
```

### First, main effect regression coefficients with PIPs

```{r}
rownames(npb.sum$main.effects) <- colnames(X.scaled[,-c(3)])
npb.sum$main.effects

```

### Next, posterior means and CIs for covariates

```{r}
rownames(npb.sum$covariates)[2:nrow(npb.sum$covariates)] <- colnames(W.scaled2)
npb.sum$covariates
```

### Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum$interactions
```

### Predict fitted values for each individual

```{r}
pred.npb <- predict(fit.npb)
fittedvals <- pred.npb$fitted.vals
```

### Plot predicted outcomes against "measured" outcomes

```{r}
plot(fittedvals, Y)
abline(a = 0, b = 1, col = "red")
```

## Run the NPB model with temperaure and ozone

Below I've used the set of priors labeled "24" and set ```scaleY = T```

The priors are as follows:
```r priors.npb.24```

Note that this version of the model **does not** include gest_age_w. It does include an indicator variable for season of conception (ref = winter) and the lon/lat as covariates and the percentage of the census tract population that is not NHW as an exposure.

```{r}
priors.npb <- priors.npb.24

#' Exposures (minus temperature)
colnames(X.scaled)

#' Covariates
colnames(W.scaled2)

# fit.npb2 <- npb(niter = 5000, nburn = 2500, X = X.scaled, Y = Y, W = W.scaled2,
#                scaleY = TRUE,
#                priors = priors.npb, interact = TRUE, XWinteract = TRUE)
# save(fit.npb2, file = here::here("Results", "NPB_Birth_Weight_v4.2.rdata"))

load(here::here("Results", "NPB_Birth_Weight_v4.2.rdata"))
npb.sum2 <- summary(fit.npb2)
```

### First, main effect regression coefficients with PIPs

```{r}
rownames(npb.sum2$main.effects) <- colnames(X.scaled)
npb.sum2$main.effects

```

### Next, posterior means and CIs for covariates

```{r}
rownames(npb.sum2$covariates)[2:nrow(npb.sum2$covariates)] <- colnames(W.scaled2)
npb.sum2$covariates
```

### Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum2$interactions
```

### Predict fitted values for each individual

```{r}
pred.npb2 <- predict(fit.npb2)
fittedvals2 <- pred.npb2$fitted.vals
```

### Plot predicted outcomes against "measured" outcomes

```{r}
plot(fittedvals2, Y)
abline(a = 0, b = 1, col = "red")
```

## Fit the NPB model without ozone and with temperature

Only ozone shows up in the NPB model. However, there is some speculation that ozone is just a proxy for some of the other variables. Here I am running the NPB model without ozone but with temperature just to see if something else pops up instead.

```{r}
priors.npb <- priors.npb.24

#' Exposures
colnames(X.scaled)

#' Covariates
colnames(W.scaled2)

# fit.npb3 <- npb(niter = 5000, nburn = 2500, X = X.scaled[,-c(2)], Y = Y, W = W.scaled2,
#                 scaleY = TRUE,
#                 priors = priors.npb, interact = TRUE, XWinteract = TRUE)
# save(fit.npb3, file = here::here("Results", "NPB_Birth_Weight_v4.3.rdata"))

load(here::here("Results", "NPB_Birth_Weight_v4.3.rdata"))
npb.sum3 <- summary(fit.npb3)
```

### First, main effect regression coefficients with PIPs

```{r}
rownames(npb.sum3$main.effects) <- colnames(X.scaled[,-c(2)])
npb.sum3$main.effects

```

### Next, posterior means and CIs for covariates

```{r}
rownames(npb.sum3$covariates)[2:nrow(npb.sum3$covariates)] <- colnames(W.scaled2)
npb.sum3$covariates
```

### Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum3$interactions
```

### Predict fitted values for each individual

```{r}
pred.npb3 <- predict(fit.npb3)
fittedvals3 <- pred.npb3$fitted.vals
```

### Plot predicted outcomes against "measured" outcomes

```{r}
plot(fittedvals3, Y)
abline(a = 0, b = 1, col = "red")
```

## Fit the NPB model without ozone and without temperature

Only ozone shows up in the NPB model. However, there is some speculation that ozone is just a proxy for some of the other variables. Here I am running the NPB model without ozone or temperature just to see if something else pops up instead.

```{r}
priors.npb <- priors.npb.24

#' Exposures
colnames(X.scaled)

#' Covariates
colnames(W.scaled2)

# fit.npb4 <- npb(niter = 5000, nburn = 2500, X = X.scaled[,-c(2,3)], Y = Y, W = W.scaled2,
#                 scaleY = TRUE,
#                 priors = priors.npb, interact = TRUE, XWinteract = TRUE)
# save(fit.npb4, file = here::here("Results", "NPB_Birth_Weight_v4.4.rdata"))

load(here::here("Results", "NPB_Birth_Weight_v4.4.rdata"))
npb.sum4 <- summary(fit.npb4)
```

### First, main effect regression coefficients with PIPs

```{r}
rownames(npb.sum4$main.effects) <- colnames(X.scaled[,-c(2,3)])
npb.sum4$main.effects

```

### Next, posterior means and CIs for covariates

```{r}
rownames(npb.sum4$covariates)[2:nrow(npb.sum4$covariates)] <- colnames(W.scaled2)
npb.sum4$covariates
```

### Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum4$interactions
```

### Predict fitted values for each individual

```{r}
pred.npb4 <- predict(fit.npb4)
fittedvals4 <- pred.npb4$fitted.vals
```

### Plot predicted outcomes against "measured" outcomes

```{r}
plot(fittedvals4, Y)
abline(a = 0, b = 1, col = "red")
```

# Linear models for each predictor

## Screening the exposures
Here I'm going to loop through some linear regression models to see if anything shows up here.
Remember that the exposure and covariates have all been scaled.

The standard deviation of the ```mean_o3``` variable is ```r round(sd(hs_data2$mean_o3),2)``` ppb

```{r}

lm_results <- data.frame()

for(i in 1:length(colnames(X.scaled))) {
  lm_df <- as.data.frame(cbind(Y, X.scaled[,i], W.scaled2))
  names(lm_df)[2] <- colnames(X.scaled)[i]
  
  ad_lm <- lm(birth_weight ~ ., data = lm_df)
  
  temp <- data.frame(exp = colnames(X.scaled)[i],
                     beta = summary(ad_lm)$coefficients[2,1],
                     beta.se = summary(ad_lm)$coefficients[2,2],
                     p.value = summary(ad_lm)$coefficients[2,4])
  temp$lcl <- temp$beta - 1.96*temp$beta.se
  temp$ucl <- temp$beta + 1.96*temp$beta.se
  lm_results <- bind_rows(lm_results, temp)
  rm(temp)
}

lm_results
write_csv(lm_results, here::here("Results", "LM_Effects_Birth_Weight_v4.csv"))
```

# Linear model with the ozone and temperature predictors

The standard deviation of the ```mean_o3``` variable is ```r round(sd(hs_data2$mean_o3),2)``` ppb
The standard deviation of the ```mean_temp``` variable is ```r round(sd(hs_data2$mean_temp),2)``` degrees F

```{r}

lm_df <- as.data.frame(cbind(Y, X.scaled[, c("mean_o3", "mean_temp")], W.scaled2))
names(lm_df)
#names(lm_df)[2] <- "mean_o3"

head(lm_df)
```

```{r}
bw_lm <- lm(birth_weight ~ mean_o3 + mean_temp + mean_o3*mean_temp +
              lat + lon + lat_lon_int +
              latina_re + black_re + other_re + 
              ed_no_hs + ed_hs + ed_aa + ed_4yr + 
              low_bmi + ovwt_bmi + obese_bmi + 
              concep_spring + concep_summer + concep_fall +
              concep_2010 + concep_2011 + concep_2012 + concep_2013 +
              maternal_age + any_smoker + smokeSH + 
              mean_cpss + mean_epsd + male,
              data = lm_df)

summary(bw_lm)
```

```{r}
plot(bw_lm)
```

# Try a GAM with the ozone and temperature predictor

The NPB model above indicates that there might be a signal for ozone. None of the other exposures had a PIP > 0.5. Here I've got a GAM with a smoothing term for ozone and temperature to see about potential nonlinear effects

The mean and standard deviation of the ```mean_o3``` variable are ```r round(mean(hs_data2$mean_o3),2)``` (```r round(sd(hs_data2$mean_o3),2)```) ppb
The mean and standard deviation of the ```mean_temp``` variable is ```r round(mean(hs_data2$mean_temp),2)``` (```r round(sd(hs_data2$mean_temp),2)```) degrees F

```{r}
library(mgcv)
library(tidymv)

gam_df <- as.data.frame(cbind(Y, X.scaled[, c("mean_o3", "mean_temp")], W.scaled2))
names(gam_df)
#names(gam_df)[2] <- "mean_o3"

head(gam_df)
```

```{r}

bw_gam <- gam(birth_weight ~ s(mean_o3, mean_temp) +
                lat + lon + lat_lon_int +
                latina_re + black_re + other_re + 
                ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                low_bmi + ovwt_bmi + obese_bmi + 
                concep_spring + concep_summer + concep_fall +
                concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                maternal_age + any_smoker + smokeSH + 
                mean_cpss + mean_epsd + male,
              data = gam_df, method = "REML")
gam.check(bw_gam)
summary(bw_gam)

save(gam_df, bw_gam, file = here::here("Results", "BW_GAM_v4.rdata"))
```

```{r}

library(mgcViz)
gam_b <- getViz(bw_gam)
plot(sm(gam_b, 1)) + 
  l_fitRaster() + l_fitContour() + l_points() +
  labs(title = NULL, x = "Ozone (scaled)", y = "Temperature (scaled)") +
  guides(fill=guide_legend(title="Change in\nbirth weight (g)")) +
ggsave(filename = here::here("Figs", "Ozone_Temp_GAM_Birth_Weight_v4.jpeg"),
       device = "jpeg", width = 5, height = 3, units = "in", dpi = 500)  
```

# GAM Sensitivity Analysis

The previous GAM suggested a possible nonlinear relationship between ozone and birth weight. However, this might be the influence of abnormally high and low exposures.

Therefore, Ander suggested a sensitivity analysis where we excluded the top and bottom 2.5% of data and just use the middle 95%.


```{r}
library(mgcv)

gam_df <- as.data.frame(cbind(Y, X.scaled[, c("mean_o3", "mean_temp")], W.scaled2))
names(gam_df)
head(gam_df)

gam_df2 <- gam_df %>%
  filter(mean_o3 > -2 & mean_o3 < 2) %>%
  filter(mean_temp > -2 & mean_temp < 2)
hist(gam_df2$mean_o3)
hist(gam_df2$mean_temp)
```

```{r}
bw_gam2 <- gam(birth_weight ~ s(mean_o3, mean_temp) + 
                lat + lon + lat_lon_int +
                latina_re + black_re + other_re + 
                ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                low_bmi + ovwt_bmi + obese_bmi + 
                concep_spring + concep_summer + concep_fall +
                concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                maternal_age + any_smoker + smokeSH + 
                mean_cpss + mean_epsd + male,
              data = gam_df2, method = "REML")
gam.check(bw_gam2)
summary(bw_gam2)

save(gam_df2, bw_gam2, file = here::here("Results", "BW_GAM_Sensitivity_v4.rdata"))
```

```{r}
library(mgcViz)
gam_b2 <- getViz(bw_gam2)
plot(sm(gam_b2, 1)) + 
  l_fitRaster() + l_fitContour() + l_points() +
  labs(title = NULL, x = "Ozone (scaled)", y = "Temperature (scaled)") +
  guides(fill=guide_legend(title="Change in\nbirth weight (g)"))
ggsave(filename = here::here("Figs", "Ozone_Temp_GAM_Birth_Weight_Sensitivity_v4.jpeg"),
       device = "jpeg", width = 5, height = 3, units = "in", dpi = 500) 
```







