---
title: "BKMR model for birth weight"
author: "Sheena Martenies"
date: "7/6/2020"
output: html_document
---

This document summarizes the prelimiary results of the Bayesian Kernel Machine Regression (BKMR) model for birth weight.

For this analysis, we take a subset of those predictors (as selected using the NPB model) and fit a BKMR model to assess independent and joint effects of the exposures. When implementing the NPB model, We used a (conservative) PIP of 0.4 determine which exposures would carry over to the BKMR model. See 07_NPB_Model_BW_MD for more details.

Based on our BEAMERS discussion, I'm going to leave gestational age out of the model, as it's likely on the causal pathway.

Read in the dataset and select the exposures and covariates

```{r , include = F, echo = F}
knitr::opts_chunk$set(echo = T, include = T, warning = F)
library(sf)
library(raster)
library(ggplot2)
library(ggthemes)
library(stringr)
library(tidyverse)
library(lubridate)
library(readxl)
library(viridis)
library(bkmr)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(family="Calibri",size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
windowsFonts(Calibri=windowsFont("TT Calibri"))
options(scipen = 9999) #avoid scientific notation

geo_data <- "R:/RSTOR-Magzamen/Research/Secondary_Data/ACS_Geodatabases/"
utm_13 <- "+init=epsg:26913"
albers <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
ll_nad83 <- "+proj=longlat +datum=NAD83 +no_defs +ellps=GRS80 +towgs84=0,0,0"
ll_wgs84 <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

```

Read in the dataset and select the exposures and covariates
```{r}
#' =============================================================================
#' Project: ECHO Aim 1 CEI BKMR Anayysis
#' Author: Sheena Martenies
#' Contact: Sheena.Martenies@colostate.edu
#' 
#' This project is a follow up the the CEI paper (Env Epi, 2018). Here we're 
#' using BKMR to identify which exposures are driving the associations reported
#' in that original paper
#' 
#' Date Created: October 21, 2019
#' 
#' Description: Using Jennifer Bobb's package to run the BKMR 
#' =============================================================================

#' Read in the clean dataset
hs_data <- read_csv(here::here("Data", "HS_Clean_Data.csv"))
nrow(hs_data)

hs_data2 <- filter(hs_data, include == 1) %>% 
  select(
    #' Exposures
         mean_pm, mean_o3, pct_tree_cover, pct_impervious,
         mean_aadt_intensity, dist_m_tri:dist_m_mine_well, 
         cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
         pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov,
         
    #' Covariates     
         latina_re, black_re, other_re, 
         ed_no_hs, ed_hs, ed_aa, ed_4yr, 
         low_bmi, ovwt_bmi, obese_bmi,
         maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
         male, 
    
    #' Outcome 
         birth_weight) %>% 
  na.omit()
nrow(hs_data2)
names(hs_data2)

exp_names <- colnames(hs_data2)[1:19]
```

Complete outcome, exposure, and covariate data are available for `r paste0(round((nrow(hs_data2)/nrow(hs_data))*100), 1, "%")` of the HS1 population.

Here we're going to try all of the exposures and drop gestational age (since it might be a mediator)

```{r}
#' ----------------------------------------------------------------------------
#' Bayesian Kernel Machine Regression: Birth weight
#' ----------------------------------------------------------------------------

hs_data3 <- select(hs_data2, 
              #' Exposures
                  mean_pm, mean_o3, pct_tree_cover, pct_impervious,
                  mean_aadt_intensity, dist_m_tri:dist_m_mine_well, 
                  cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
                  pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov,
              
              #' Covariates
                  latina_re, black_re, other_re,
                  ed_no_hs, ed_hs, ed_aa, ed_4yr,
                  low_bmi, ovwt_bmi, obese_bmi,
                  maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
                  male, 

              #' Outcome
                  birth_weight)
names(hs_data3)

ncol(hs_data2)
ncol(hs_data3)

y <- hs_data3$birth_weight
Z <- as.matrix(select(hs_data3, all_of(exp_names)))
X <- as.matrix(select(hs_data3, latina_re, black_re, other_re, 
                      ed_no_hs, ed_hs, ed_aa, ed_4yr, 
                      low_bmi, ovwt_bmi, obese_bmi,
                      maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
                      male))

#' Scale these variables
y.scaled <- scale(y)
Z.scaled <- apply(Z, 2, scale)

X.s <- apply(X[,c(11, 14, 15)], 2, scale) #' just the continuous ones

X.scaled <- cbind(X[,1:10], X.s[,1],
                  X[,12:13], X.s[,2:3],
                  X[,16])
colnames(X.scaled)
colnames(X.scaled) <- colnames(X) 
```

Before running, I checked to ensure there was sufficient variability in the exposures and covariates. What does the outcome (birth weight) look like?
```{r , include = T, echo = T}
var(Z.scaled)
var(X.scaled)

hist(y, main = "Birth weight (unscaled)")
hist(y.scaled, main = "Birth weight (scaled)")
```

Fitting the BKMR model and investigating model convergence

```{r , include = FALSE, echo = T}
# Fit the BKMR model using the scaled variables
set.seed(123)

# fitkm.1 <- kmbayes(y = y.scaled, Z = Z.scaled, X = X.scaled, iter = 10000,
#                  verbose = FALSE, varsel = TRUE)

#' Save current results
# save(fitkm.1, y, y.scaled, Z, Z.scaled, X, X.scaled,
#      file = here::here("Results", "BKMR_Model_BW_v2.rdata"))

load(file = here::here("Results", "BKMR_Model_BW_v2.rdata"))
```

```{r , include = T, echo = F}
fitkm.1
names(fitkm.1)

TracePlot(fit = fitkm.1, par = "beta")
TracePlot(fit = fitkm.1, par = "sigsq.eps")
TracePlot(fit = fitkm.1, par = "r", comp = 1)
```

What do the posterior inclusion probabilities (PIPs) look like?

```{r , include = T, echo = F}
#' Show the estimated posterior inclusion probabilities
#' PIPs are the proportion of iterations that include the predictor
#' Higher PIP means higher chance of it being in the model

arrange(ExtractPIPs(fitkm.1), desc(PIP))
```

How does h(z) compare when using the three different approaches?

```{r , include = F, echo = T}
#' Estimate h(z) using three different approaches
#' Need to specify at what level of exposure we are estimating h(z)
#' Using median exposures for now

med_vals <- apply(Z.scaled, 2, median) #' medians for all exposures
med_vals

Znew <- matrix(med_vals, nrow = 1) #' matrix of exposure medians 
Znew

#' Approach 1: estimates the posterior mean as μh(θ^) and the posterior variance 
#' as Vh(θ^) where θ^ is the posterior mean estimate of θ. 

h_est1 <- ComputePostmeanHnew(fitkm.1, Znew = Znew, method = "approx")
h_est1

#' Approach 2: estimates the posterior mean as E[μh(θ)] by taking the mean of 
#' posterior samples of μh(θ), and the posterior variance as E[Vh(θ)]+Var[μh(θ)] 
#' by taking the mean of the posterior samples of Vh(θ) and the variance of the 
#' posterior samples of μh(θ) and them summing these quantities. 

h_est2 <- ComputePostmeanHnew(fitkm.1, Znew = Znew, method = "exact")
h_est2

#' Approach 3: Approach 3: generates posterior samples of h(z) by sampling 
#' h∼N(μh(θ),Vh(θ)), given particular samples of θ from the fitted BKMR model
#' NOTE: This is the slowest version but it allows you to estimate the full
#' posterior distribution of h(z)

Xnew <- matrix(0, nrow = 1, ncol = ncol(X))
samps3 <- SamplePred(fitkm.1, Znew = Znew, Xnew = Xnew)

#' Compare the three results
h_est_compare <- data.frame(
  method = c(1:3),
  post_mean = c(h_est1$postmean, h_est2$postmean, mean(samps3)),
  post_sd = c(sqrt(h_est1$postvar), sqrt(h_est2$postvar), sd(samps3))
)
h_est_compare
```

```{r , include = T, echo = T}
h_est_compare
```

Summarize the BKMR model output: Exposure-response curves for each exposure while holding the others at their 25th, 50th, or 75th percentiles

```{r , include = T, echo = F}

#' First, get the univariate relationships
pred.resp.univar.50 <- PredictorResponseUnivar(fit = fitkm.1)
pred.resp.univar.25 <- PredictorResponseUnivar(fit = fitkm.1, q.fixed = 0.25)
pred.resp.univar.75 <- PredictorResponseUnivar(fit = fitkm.1, q.fixed = 0.75)

pred.resp.univar.50
pred.resp.univar.25
pred.resp.univar.75

#' Then, plot using ggplot
ggplot(pred.resp.univar.50, aes(z, est, ymin = est - 1.96*se, ymax = est + 1.96*se)) + 
  geom_smooth(stat = "identity") + 
  facet_wrap(~ variable) +
  ylab("h(z) holding other variables at 50th percentile")

ggplot(pred.resp.univar.25, aes(z, est, ymin = est - 1.96*se, ymax = est + 1.96*se)) + 
  geom_smooth(stat = "identity") + 
  facet_wrap(~ variable) +
  ylab("h(z) holding other variables at 25th percentile")

ggplot(pred.resp.univar.75, aes(z, est, ymin = est - 1.96*se, ymax = est + 1.96*se)) + 
  geom_smooth(stat = "identity") + 
  facet_wrap(~ variable) +
  ylab("h(z) holding other variables at 75th percentile")
```

Summarize the BKMR model output: Bivariate relationships between two predictors while holding the others at their 25th, 50th, or 75th percentiles

```{r , include = T, echo = F}
pred.resp.bivar.50 <- PredictorResponseBivar(fit = fitkm.1, min.plot.dist = 1)
pred.resp.bivar.50

ggplot(pred.resp.bivar.50, aes(z1, z2, fill = est)) + 
  geom_raster() + 
  facet_grid(variable2 ~ variable1) +
  scale_fill_viridis() +
  # scale_fill_gradientn(colours=c("#0000FFFF","#FFFFFFFF","#FF0000FF")) +
  xlab("expos1") +
  ylab("expos2") +
  ggtitle("h(expos1, expos2)")

pred.resp.bivar.levels.50 <- PredictorResponseBivarLevels(
  pred.resp.df = pred.resp.bivar.50, 
  Z = Z.scaled, qs = c(0.1, 0.5, 0.9))

ggplot(pred.resp.bivar.levels.50, aes(z1, est)) + 
  geom_smooth(aes(col = quantile), stat = "identity") + 
  facet_grid(variable2 ~ variable1) +
  scale_color_viridis(discrete = T) +
  ggtitle("h(expos1 | quantiles of expos2)") +
  xlab("expos1")
```

Summarize the BKMR model output: plotting the overall effect size for each percentile relative to the 50th percentile

```{r , include = T, echo = F}

risks.overall <- OverallRiskSummaries(fit = fitkm.1, y = y.scaled, 
                                      Z = Z.scaled, X = X.scaled, 
                                      qs = seq(0.25, 0.75, by = 0.05), 
                                      q.fixed = 0.5, method = "exact")
risks.overall

ggplot(risks.overall, aes(quantile, est, ymin = est - 1.96*sd, ymax = est + 1.96*sd)) + 
  xlab("Exposure quantile") +
  ylab("Effect estimate") +
  geom_pointrange()
```

Summarize the BKMR model output: Estimate the risks for the individual variables the exposure is at the 75th percentile relative to the 25th percentile (essentially an IQR increase), holding all other exposures at the 25th, 50th, and 75th percentiles

```{r , include = T, echo = F}

risks.singvar <- SingVarRiskSummaries(fit = fitkm.1, y = y.scaled, 
                                      Z = Z.scaled, X = X.scaled, 
                                      qs.diff = c(0.25, 0.75), 
                                      q.fixed = c(0.25, 0.50, 0.75),
                                      method = "exact")
risks.singvar

ggplot(risks.singvar, aes(variable, est, ymin = est - 1.96*sd, 
                          ymax = est + 1.96*sd, col = q.fixed)) + 
  scale_color_viridis(discrete = T) +
  geom_pointrange(position = position_dodge(width = 0.75)) + 
  coord_flip()
```

Checking for interation: by how much do the effect sizes for each expsoure change when we increase all the other exposures from the 25th to the 75th percentiles

```{r , include = T, echo = F}

risks.int <- SingVarIntSummaries(fit = fitkm.1, y = y.scaled, 
                                 Z = Z.scaled, X = X.scaled, 
                                 qs.diff = c(0.25, 0.75), 
                                 qs.fixed = c(0.25, 0.75),
                                 method = "exact")
risks.int


ggplot(risks.int, aes(variable, est, ymin = est - 1.96*sd, 
                      ymax = est + 1.96*sd, col = variable)) + 
  scale_color_viridis(discrete = T) +
  geom_pointrange(position = position_dodge(width = 0.75)) + 
  coord_flip()
```

Save these results

```{r , include = T, echo = F}
save(pred.resp.univar.25, pred.resp.univar.50, pred.resp.univar.75,
     pred.resp.bivar.25, pred.resp.bivar.50, pred.resp.bivar.75,
     pred.resp.bivar.levels.50,
     risks.overall, risks.singvar, risks.int,
     file = here::here("Results", "BKMR_Model_BW_Results_v2.rdata"))
```
