---
title: "Preliminary NPB Model for Adiposity"
author: "Sheena Martenies"
date: "07/20/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r, include = F}
#' -----------------------------------------------------------------------------
#' Install the new version of the package
#' -----------------------------------------------------------------------------

# library(devtools)
# install_github("lvhoskovec/mmpack", build_vignettes = TRUE, force = TRUE)

library(tidyverse)
library(lubridate)
library(haven)
library(readxl)
library(mmpack)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(family="Calibri",size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
# windowsFonts(Calibri=windowsFont("TT Calibri"))
options(scipen = 9999) #avoid scientific notation

```

This version of the adiposity analysis mirrors the birth weight analysis from ```09_NPB_Model_BW_v3_MD.R```

Some key findings to note:

- There are fewer participants with complete data on the adiposity outcome and covariates of interest


# Exploring the data set

The HS data set was previously used in the CEI paper (Martenies et al., 2019). In the original analysis, we used an exposure index based on the CalEnvironScreen tool. We observed lower birth weights and lower adiposity associated with higher index scores, driven largely by exposures to social indicators of health at the neighborhood level. Now, we are aiming to use methods for mixtures to try to identify which exposures are driving these association.

```{r, echo = T, include = F}

#' Read in the clean dataset
hs_data <- read_csv(here::here("Data", "HS_Clean_Data.csv")) %>% 
  filter(!is.na(conception_date))
nrow(hs_data)

#' Add some additional variables
hs_data$lat_lon_int <- hs_data$lat * hs_data$lon
hs_data$concep_year <- year(hs_data$conception_date)

unique(hs_data$concep_year)

hs_data$concep_2009 <- ifelse(hs_data$concep_year == "2009", 1, 0)
hs_data$concep_2010 <- ifelse(hs_data$concep_year == "2010", 1, 0)
hs_data$concep_2011 <- ifelse(hs_data$concep_year == "2011", 1, 0)
hs_data$concep_2012 <- ifelse(hs_data$concep_year == "2012", 1, 0)
hs_data$concep_2013 <- ifelse(hs_data$concep_year == "2013", 1, 0)

hs_data2 <- filter(hs_data, include == 1) %>% 
  select(
    #' Exposures
    mean_pm, mean_o3, pct_tree_cover, pct_impervious,
    mean_aadt_intensity, dist_m_tri:dist_m_mine_well, 
    cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
    pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov, pct_poc,
    
    #' Covariates     
    lon, lat, lat_lon_int, 
    latina_re, black_re, other_re, #' ref is white_re
    ed_no_hs, ed_hs, ed_aa, ed_4yr, #' ref is ed_grad
    low_bmi, ovwt_bmi, obese_bmi, #' ref is norm_bmi
    concep_spring, concep_summer, concep_fall, #' ref is concep_winter
    concep_2010, concep_2011, concep_2012, concep_2013, #ref is concep_2009
    maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
    male, gest_age_w, days_to_peapod,
    
    #' Outcomes 
    adiposity) %>% 
  na.omit()
```

The complete data set for the adiposity outcome consists of n =  `r nrow(hs_data2)` participants. This represents `r paste0(round((nrow(hs_data2)/ nrow(hs_data)*100),2), "%")` of the original Healthy Start 1 cohort.

Of the `r nrow(hs_data2)` participants, `r round(sum(hs_data2$latina_re)/nrow(hs_data2),2)`% identify as Latina, `r round(sum(hs_data2$black_re)/nrow(hs_data2),2)`% identify as Black, and `r round(sum(hs_data2$latina_re)/nrow(hs_data2),2)`% identify as another non-NHW race or ethnicity. The median age of mothers in this dataset is `r round(median(hs_data2$maternal_age),2)` years.  `r round(sum(hs_data2$male)/nrow(hs_data2),2)`% of babies born were male.  

## Exposure data

We have included `r ncol(select(hs_data2, mean_pm:pct_hh_pov))` exposures in our analysis. 

These exposures are based on the census tract where each mother lived at the time of enrollment into Healthy Start. With the exception of air pollution (mean_pm and mean_o3), these are based on long-term averages at for each census tract. For mean_pm and mean_o3 are based on the average pollution levels across each pregnancy (est. conception date to delivery date) estimated using ordinary kriging and monitoring data.

```{r}
#' Exposure data
X <- select(hs_data2, mean_pm, mean_o3, pct_tree_cover, pct_impervious,
            mean_aadt_intensity, dist_m_tri:dist_m_mine_well,
            cvd_rate_adj, res_rate_adj, violent_crime_rate, property_crime_rate,
            pct_less_hs, pct_unemp, pct_limited_eng, pct_hh_pov, pct_poc) %>%
  as.matrix()
head(X)
```

Variance and histograms of the exposure variables (in their original units):

```{r}
var(X)
ggplot(pivot_longer(as.data.frame(X), mean_pm:pct_poc, names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

Scaling the exposure variables

```{r}
X.scaled <- apply(X, 2, scale)
head(X.scaled)
```

Variance and histograms of the exposure variables (scaled):

```{r}
var(X.scaled)
ggplot(pivot_longer(as.data.frame(X.scaled), mean_pm:pct_poc, 
                    names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

## Covariate data

Covariates were assessed at the individual level. These were selected based on previous HS studies and others in the literature and informed by a DAG.

NOTE: It'll be interesting to see what comes out of our BEAMERS discussion re: adjusting for gestational age. It's currently in the analysis

There are four continuous covariates; all of the others have been coded as dummy variables. For the dummy variables, the reference groups are: white_re, ed_grad, norm_bmi

```{r}
W <- select(hs_data2, 
            lat, lon, lat_lon_int,
            latina_re, black_re, other_re,
            ed_no_hs, ed_hs, ed_aa, ed_4yr,
            low_bmi, ovwt_bmi, obese_bmi,
            concep_spring, concep_summer, concep_fall,
            concep_2010, concep_2011, concep_2012, concep_2013,
            maternal_age, any_smoker, smokeSH, mean_cpss, mean_epsd,
            male, gest_age_w, days_to_peapod) %>%
  as.matrix()
head(W)
```

Scaled the non-binary (continuous) covariates

```{r}
colnames(W)
W.s <- apply(W[,c(1, 2, 3, 21, 24, 25, 27, 28)], 2, scale) #' just the continuous ones

W.scaled <- cbind(W.s[,1:3],
                  W[,4:20], W.s[,4],
                  W[,22:23], W.s[,5:6],
                  W[,26], W.s[,7:8])
colnames(W.scaled)
colnames(W.scaled) <- colnames(W)
head(W.scaled)
summary(W.scaled)
```

Variance and histograms for the scaled covariates

```{r}
var(W.scaled)

ggplot(pivot_longer(as.data.frame(W.scaled), lat:gest_age_w, 
                    names_to = "exp", values_to = "value")) + 
    geom_histogram(aes(x = value)) + 
    facet_wrap(~ exp, scales = "free")
```

## Response data: adiposty (%fat mass)

```{r}
Y <- select(hs_data2, adiposity) %>%
  as.matrix()
head(Y)
```

Distribution of adiposity and scaled adiposity

```{r}
hist(Y, breaks = 20)
hist(scale(Y), breaks = 20)
```

## Scatterplots of exposures and outcome (adiposity)

Both adiposity (Y) and the exposures are scaled here

**NOTE**: Don't use these plots as a way to estimate how many predictors might make the cut. This should be done a priori

```{r}
df <- as.data.frame(cbind(scale(Y), X.scaled))
# par(mfrow=c(5,4))
sapply(2:length(df), function(x){
  lm.x <- lm(adiposity ~ df[,x], data = df)
  plot(df[,c(x, 1)],
       xlab = paste0(colnames(df)[x], " beta: ",
                     round(summary(lm.x)$coef[2,1],4),
                     "; p = ",
                     round(summary(lm.x)$coef[2,4],4)))
  abline(lm.x)
})
```

# Is gestational age a potenital mediator?

I.e., is there a relationship between our exposures and gestational age?

The DAG might look something like this:

exposures ---> gestational age ---> adiposity
     \_________________________________^

## Scatter plots for exposures and gestational age

Both gestational age and the exposures are scaled here.
Gestational age measured in weeks from estimated date of conception to delivery

Since there were some (small) relationships between exposures and gestational age (based on simple linear regression models-- namely the ozone and SES indicators), I'm going to omit this covariate for now. 

```{r}
df2 <- as.data.frame(cbind(W.scaled[,"gest_age_w"], X.scaled))
colnames(df2)[1] <- "gest_age_w"
# par(mfrow=c(5,4))
sapply(2:length(df2), function(x){
  lm.x <- lm(gest_age_w ~ df2[,x], data = df2)
  plot(df2[,c(x, 1)],
       xlab = paste0(colnames(df2)[x], " beta: ",
                     round(summary(lm.x)$coef[2,1],4),
                     "; p = ",
                     round(summary(lm.x)$coef[2,4],4)))
  abline(lm.x)
})
```

Dropping gest_age_w from the covariates

```{r}
colnames(W.scaled)
W.scaled2 <- W.scaled[,-c(ncol(W.scaled)-1)]
colnames(W.scaled2)
```

# RIDGE regression

To see if there might be something going on, Lauren suggested a ridge regression with a small penalty.

```{r}
set.seed(123)

library(glmnet)

lambda_seq <- 10^seq(4, -4, by = -.05)

#' Best lambda from CV
ridge_cv <- cv.glmnet(X, Y, alpha = 0, lambda = lambda_seq,
                      standardize = T, standardize.response = T)
plot(ridge_cv)
best_lambda <- ridge_cv$lambda.min
best_lambda

#' Fit the model using the best_lambda
ad_ridge <- glmnet(X, Y, alpha = 0, lambda = best_lambda,
                   standardize = T, standardize.response = T)
summary(ad_ridge)
```

Ridge regression coefficients

```{r}
coef(ad_ridge)
```

Ridge regression predictions

```{r}
ridge_pred <- predict(ad_ridge, newx = X)
plot(Y, ridge_pred)

actual <- Y
preds <- ridge_pred
rsq <- 1 - (sum((preds - actual) ^ 2))/(sum((actual - mean(actual)) ^ 2))
```

The R2 value for this model is `r round(rsq, 2)`. Based on these results, it doesn't look like there's much here.

# Nonparametric Bayesian Shrinkage (NPB): Adiposity

Still, we wanted to try to fit the NPB model with these data.

## Finding the NPB priors

I'm starting with the sets of priors used in the birth weight analysis.
**Note**: I'm including far fewer iterations of the priors than in the previous version of the document.

### Vignette Priors

```{r}
set.seed(123)

priors.npb.1 <- list(alpha.pi = 1, beta.pi = 1, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1)

fit.npb.1 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.1, interact = F)
npb.sum.1 <- summary(fit.npb.1)
npb.sum.1$main.effects
plot(fit.npb.1$beta[,1], type = "l")
plot(fit.npb.1$beta[,2], type = "l")
plot(fit.npb.1$beta[,13], type = "l")
```

### Adjust alpha.pi and beta.pi

For now, leave a.phi1 and sig2inv.mu1 alone for now.

alpha.pi and beta.pi are responisble for the exclusion probability distribution.
If we thing we want ~50% of our covariates, we need the mass of this distribution to be somewhere between 0.4 and 0.6. To do this, we set alpha.pi and beta.pi to the same value

#### Try making alpha.pi and beta.pi 2

```{r}
plot(density(rbeta(10000, 2, 2)))

priors.npb.12 <- list(alpha.pi = 2, beta.pi = 2, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.12 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.12, interact = F)
npb.sum.12 <- summary(fit.npb.12)
npb.sum.12$main.effects
plot(fit.npb.12$beta[,1], type = "l")
plot(fit.npb.12$beta[,2], type = "l")
plot(fit.npb.12$beta[,13], type = "l")
```

#### Try making alpha.pi and beta.pi 5

```{r}
plot(density(rbeta(10000, 5, 5)))

priors.npb.13 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.13 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.13, interact = F)
npb.sum.13 <- summary(fit.npb.13)
npb.sum.13$main.effects
plot(fit.npb.13$beta[,1], type = "l")
plot(fit.npb.13$beta[,2], type = "l")
plot(fit.npb.13$beta[,13], type = "l")
```

#### Try making alpha.pi and beta.pi 8

```{r}
plot(density(rbeta(10000, 8, 8)))

priors.npb.14 <- list(alpha.pi = 8, beta.pi = 8, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 1, sig2inv.mu1 = 1)

fit.npb.14 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.14, interact = F)
npb.sum.14 <- summary(fit.npb.14)
npb.sum.14$main.effects
plot(fit.npb.14$beta[,1], type = "l")
plot(fit.npb.14$beta[,2], type = "l")
plot(fit.npb.14$beta[,13], type = "l")
```

### Set alpha.pi and beta.pi to 5, readjust a.phi1 and sig2inv.mu1

Set alpha.pi and beta.pi to 5, rather than 8, and try adjusting a.phi1 and sig2inv.mu1

#### Try making a.phi1 = 10 and sig2inv.mu1 = 1

```{r}
priors.npb.23 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 1)

fit.npb.23 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.23, interact = F)
npb.sum.23 <- summary(fit.npb.23)
npb.sum.23$main.effects
plot(fit.npb.23$beta[,1], type = "l")
plot(fit.npb.23$beta[,2], type = "l")
plot(fit.npb.23$beta[,13], type = "l")
```

#### Try making a.phi1 = 10 and sig2inv.mu1 = 10

```{r}
priors.npb.24 <- list(alpha.pi = 5, beta.pi = 5, alpha.pi2 = 9, beta.pi2 = 1,
                     a.phi1 = 10, sig2inv.mu1 = 10)

fit.npb.24 <- npb(niter = 1000, nburn = 500, X = X.scaled, Y = Y, W = W.scaled2,
                 scaleY = TRUE,
                 priors = priors.npb.24, interact = F)
npb.sum.24 <- summary(fit.npb.24)
npb.sum.24$main.effects
plot(fit.npb.24$beta[,1], type = "l")
plot(fit.npb.24$beta[,2], type = "l")
plot(fit.npb.24$beta[,13], type = "l")
plot(fit.npb.24$beta[,15], type = "l")
```

## Fit the NPB model

As with the birth weight model, I've used the 24th set of priors and set ```scaleY = T``` in the NPB model below

The priors are as follows:
```r priors.npb.24```

Note that this version of the model does not include gest_age_w. It does include an indicator variable for season of conception (ref = winter) and the lon/lat as covariates and the percentage of the census tract population that is not NHW as an exposure

```{r}
priors.npb <- priors.npb.24

#' Exposures
colnames(X.scaled)

#' Covariates
colnames(W.scaled2)

# fit.npb <- npb(niter = 5000, nburn = 2500, X = X.scaled, Y = Y, W = W.scaled2,
#                scaleY = TRUE,
#                priors = priors.npb, interact = TRUE, XWinteract = TRUE)
# save(fit.npb, file = here::here("Results", "NPB_Adiposity_v3.rdata"))

load(here::here("Results", "NPB_Adiposity_v3.rdata"))
npb.sum <- summary(fit.npb)
```

### First, main effect regression coefficients with PIPs

```{r}
rownames(npb.sum$main.effects) <- colnames(X.scaled)
npb.sum$main.effects

npb.sum$main.effects$exp <- rownames(npb.sum$main.effects)
write_csv(as.data.frame(npb.sum$main.effects), here::here("Results", "NPB_Main_Effects_Adiposity.csv"))

#' Which one's have PIPs > 0.5
# selected_exp <- which(npb.sum$main.effects[,5] >= 0.5)
# selected_exp

```

### Next, posterior means and CIs for covariates

```{r}
rownames(npb.sum$covariates)[2:nrow(npb.sum$covariates)] <- colnames(W.scaled2)
npb.sum$covariates

npb.sum$covariates$exp <- rownames(npb.sum$covariates)
write_csv(as.data.frame(npb.sum$covariates), here::here("Results", "NPB_Covariates_Adiposity.csv"))
```

### Interactions
Next, all of the interactions between exposures or between exposures and covariates

```{r}
npb.sum$interactions
```

<!-- ### Predict fitted values for each individual -->

<!-- ```{r} -->
<!-- pred.npb <- predict(fit.npb) -->
<!-- fittedvals <- pred.npb$fitted.vals -->
<!-- ``` -->

<!-- ### Plot predicted outcomes against "measured" outcomes -->

<!-- ```{r} -->
<!-- plot(fittedvals, Y) -->
<!-- abline(a = 0, b = 1, col = "red") -->
<!-- ``` -->

# Linear models for each predictor

## Screening the exposures
None of the exposures had a PIP > 0.5. Here I'm going to loop through some linear regression models to see if anything shows up here.
Remember that the exposure and covariates have all been scaled.

```{r}

lm_results <- data.frame()

for(i in 1:length(colnames(X.scaled))) {
  lm_df <- as.data.frame(cbind(Y, X.scaled[,i], W.scaled2))
  names(lm_df)[2] <- colnames(X.scaled)[i]
  
  ad_lm <- lm(adiposity ~ ., data = lm_df)
  
  temp <- data.frame(exp = colnames(X.scaled)[i],
                     beta = summary(ad_lm)$coefficients[2,1],
                     beta.se = summary(ad_lm)$coefficients[2,2],
                     p.value = summary(ad_lm)$coefficients[2,4])
  temp$lcl <- temp$beta - 1.96*temp$beta.se
  temp$ucl <- temp$beta + 1.96*temp$beta.se
  lm_results <- bind_rows(lm_results, temp)
  rm(temp)
}

lm_results
write_csv(lm_results, here::here("Results", "LM_Effects_Adiposity.csv"))
```

## Linear model for distance to waste sites

```{r}

lm_df <- as.data.frame(cbind(Y, X.scaled, W.scaled2))

ad_waste_lm <- lm(adiposity ~ dist_m_waste_site + 
                    lat + lon + lat_lon_int +
                    latina_re + black_re + other_re + 
                    ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                    low_bmi + ovwt_bmi + obese_bmi + 
                    concep_spring + concep_summer + concep_fall +
                    concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                    maternal_age + any_smoker + smokeSH + 
                    mean_cpss + mean_epsd + male + days_to_peapod,
                    data = lm_df)

summary(ad_waste_lm)
```

```{r}
plot(ad_waste_lm)
```

## Linear model for respiratory hospitalization rates

```{r}

lm_df <- as.data.frame(cbind(Y, X.scaled, W.scaled2))

ad_res_lm <- lm(adiposity ~ res_rate_adj + 
                    lat + lon + lat_lon_int +
                    latina_re + black_re + other_re + 
                    ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                    low_bmi + ovwt_bmi + obese_bmi + 
                    concep_spring + concep_summer + concep_fall +
                    concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                    maternal_age + any_smoker + smokeSH + 
                    mean_cpss + mean_epsd + male + days_to_peapod,
                    data = lm_df)

summary(ad_res_lm)
```

```{r}
plot(ad_res_lm)
```

## Linear model for property crime rates

```{r}

lm_df <- as.data.frame(cbind(Y, X.scaled, W.scaled2))

ad_pcrime_lm <- lm(adiposity ~ property_crime_rate + 
                    lat + lon + lat_lon_int +
                    latina_re + black_re + other_re + 
                    ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                    low_bmi + ovwt_bmi + obese_bmi + 
                    concep_spring + concep_summer + concep_fall +
                    concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                    maternal_age + any_smoker + smokeSH + 
                    mean_cpss + mean_epsd + male + days_to_peapod,
                    data = lm_df)

summary(ad_pcrime_lm)
```

```{r}
plot(ad_pcrime_lm)
```

## Linear model for %unemployed rates

```{r}

lm_df <- as.data.frame(cbind(Y, X.scaled, W.scaled2))

ad_unemp_lm <- lm(adiposity ~ pct_unemp + 
                    lat + lon + lat_lon_int +
                    latina_re + black_re + other_re + 
                    ed_no_hs + ed_hs + ed_aa + ed_4yr + 
                    low_bmi + ovwt_bmi + obese_bmi + 
                    concep_spring + concep_summer + concep_fall +
                    concep_2010 + concep_2011 + concep_2012 + concep_2013 +
                    maternal_age + any_smoker + smokeSH + 
                    mean_cpss + mean_epsd + male + days_to_peapod,
                    data = lm_df)

summary(ad_unemp_lm)
```

```{r}
plot(ad_unemp_lm)
```





