---
title: "A mixtures approach to assessing relationships between environmental and social determinants of health and neonatal size and body composition in the Healthy Start cohort"
author: "Sheena Martenies"
date: "08/01/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    number_sections: true
---

**A mixtures approach to assessing relationships between environmental and social determinants of health and neonatal size and body composition in the Healthy Start cohort**

Sheena E. Martenies^1^, Lauren Hoskovec^2^, Ander Wilson^2^, Brianna Moore^3^, Anne P. Starling^4,5^, William B. Allshouse^6^, John L. Adgate^6^, Dana Dabelea^4,5,7^, and Sheryl Magzamen^1,4^

^1^ Environmental and Radiological Health Sciences, Colorado State University, Fort Collins, CO USA
^2^ Statistics, Colorado State University, Fort Collins, CO USA
^3^ Brianna’s new affiliation
^4^ Epidemiology, Colorado School of Public Health, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
^5^ Lifecourse Epidemiology of Adiposity and Diabetes (LEAD Center), University of Colorado Anschutz Medical Campus, Aurora CO, USA
^6^ Environmental and Occupational Health, Colorado School of Public Health, University of Colorado Anschutz Medical Campus, Aurora, CO, USA
^7^ Pediatrics, School of Medicine, University of Colorado Anschutz Medical Campus, Aurora, CO, USA

*Corresponding Author: Sheryl.Magzamen@colostate.edu

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, include = F)
```

# Introduction

Birth weight and adiposity at birth are important neonatal indicators of infant, childhood, and long-term health. Over the past few decades, there has been an increasing trend in the frequency of babies born with low birth weight (LBW; < 2500 g) and small for gestational age (SGA; below the 10th percentile for each completed week of gestation).^1–3^ SGA and LBW babies are at higher risk of childhood obesity, asthma, delayed neurodevelopment, and metabolic disorders later in adulthood.^4–10^ Similarly, adiposity at birth, which is a measure of the proportion of body mass that is fat mass, is a potentially important obesity and metabolic disease risk later in life.^11^ 

Factors at both the individual level and the neighborhood level have been associated with birth weight and adiposity measured at birth in previous studies. Individual level factors include maternal characteristics such as age and race/ethnicity, maternal behaviors such as active smoking and physical activity, and metabolic outcomes such as obesity or gestational diabetes.^12–14^ At the neighborhood level, both environmental and social determinants of health have been linked to these neonatal characteristics. These factors include: higher neighborhood deprivation index scores,^15^ low neighborhood affluence,16 poor built environments (e.g., higher rates of vacant buildings or proximity to major roadways),^17,18^ and higher ambient air pollutant exposures.^19–23^ Together, the existing literature demonstrates the ability of both individual-level and neighborhood-level exposures to influence neonatal, childhood, and long-term health.

Although there is evidence to suggest both social and environmental determinants of health are associated with birth weight and adiposity, few studies have examined the combined effects of exposures to hazards in multiple domains (i.e., physical, social, and chemical exposures). In our previous work, we tested associations between neonatal outcomes and combined prenatal determinants of health using an index approach for assigning exposures at the neighborhood level.^24^ We reported lower birth weights and adiposity for infants born to mothers with higher combined exposure index scores after controlling for key individual-level risk confounders. However, the use of an index did not allow us to identify which exposures or combination of exposures were driving these associations. Research on the independent and joint effects of environmental and social determinants is needed to better characterize the effects of these prenatal exposures on neonatal outcomes and identify targets for future public health interventions.^25^

Here we expanded on our previous study to investigate the individual and joint effects of neighborhood-level determinants of health on neonatal outcomes in the Healthy Start birth cohort. We hypothesized that specific components of the pre-natal exposure mixture were driving associations with lower birth weight and adiposity. To test our hypothesis, we used Non-parametric Bayes Shrinkage (NPB), 




```{r}
#' -----------------------------------------------------------------------------
#' Install the new version of the package
#' -----------------------------------------------------------------------------
library(tidyverse)
library(lubridate)
library(haven)
library(readxl)
library(mmpack)

#' For ggplots
simple_theme <- theme(
  #aspect.ratio = 1,
  text  = element_text(family="Calibri",size = 12, color = 'black'),
  panel.spacing.y = unit(0,"cm"),
  panel.spacing.x = unit(0.25, "lines"),
  panel.grid.minor = element_line(color = "transparent"),
  panel.grid.major = element_line(color = "transparent"),
  panel.border=element_rect(fill = NA),
  panel.background=element_blank(),
  axis.ticks = element_line(colour = "black"),
  axis.text = element_text(color = "black", size=10),
  # legend.position = c(0.1,0.1),
  plot.margin=grid::unit(c(0,0,0,0), "mm"),
  legend.key = element_blank()
)
# windowsFonts(Calibri=windowsFont("TT Calibri"))
options(scipen = 9999) #avoid scientific notation

```

